---
title: "Running time"
author: "Hao Huang"
date: '2022-07-03'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages
```{r}
library(glue)
library(ggplot2)

```

# Plot setting1
Deep learning methods
```{r}
nn_methods = c("DeepLift", "GradientShap", "LRP" , "FeatureAblation", "Occlusion"  ,"Lime")
dl_cat <- c(rep("Deep learning - gradient based", 3), rep("Deep learning - perturbation", 3))
dl_cat_num =1
df <- data.frame()
for (method in nn_methods){
  time.res <- read.csv(glue("../../Result/Fs_marker/Nn/Setting1/{method}/Elapse_time_record.csv"))[,2]
  df <- rbind(df, cbind(time.res, rep(c(5,10,15,20), 10), rep(method,40), dl_cat[dl_cat_num]))
  dl_cat_num = dl_cat_num +1
}
colnames(df) <- c("Time", "nGroups", "Method", "Category")
df.nn <- df
```

Traditional methods
```{r}
trad_methods = c( "runDESeq2", "runLimmavoom", "runScDD")
df <- data.frame()
for (method in trad_methods){
  n=1 # seed number 
  j=1
  while(j<=10){
    for(nGroups in c(5, 10, 15, 20)){ # cell type number
        tmp_time = readRDS(glue("../../Result/Fs_marker/Traditional/Setting1/{method}/Res_{method}_Simulation_setting1_nCells_200_nGroups_{nGroups}__iteration{j}_seeds{n}.rds"))$time
        df <- rbind(df,c(tmp_time, nGroups, method, "Traditional"))
        n=n+1
        }
    j=j+1
    }
  cat(glue("finished {method}"))
  }
colnames(df) <- c("Time", "nGroups", "Method", "Category")
df.trad <- df
```

combine
```{r}
df.combine <- rbind(df.nn, df.trad)
df.combine$nGroups <- factor(df.combine$nGroups, levels = c(5,10,15,20))
df.combine$Method <- factor(df.combine$Method, levels = c(nn_methods, trad_methods))
df.combine$Time <- as.numeric(df.combine$Time)
```


```{r}
df.average <- aggregate(Time~Method+nGroups, data=df.combine, FUN=mean)
df.average
```
Line plot, coloured by methods
```{r}
p1 = ggplot(aes(x=nGroups, y=Time, color=Method), data = df.average) + geom_line(aes(group=Method)) + geom_point(aes(color=Method)) +ylab("Time(s)")  + coord_cartesian(ylim = c(0,15000))+theme_classic()
p1
ggsave(p1, width = 6, height = 4,filename=glue("../../Figures/Running_time//Setting1_TM.pdf"))
```


zoom plot for some representative methods
```{r}
p1 = ggplot(aes(x=nGroups, y=Time, color=Method), data = df.average) + geom_line(aes(group=Method)) + geom_point(aes(color=Method)) +ylab("Time(s)") + coord_cartesian(ylim = c(0,1200))+theme_classic()
p1
ggsave(p1, width = 6, height = 4,filename=glue("../../Figures/Running_time//Setting1_zoom_TM.pdf"))
```

zoom plot for some representative methods - 2
```{r}
p1 = ggplot(aes(x=nGroups, y=Time, color=Method), data = df.average) + geom_line(aes(group=Method)) + geom_point(aes(color=Method)) +ylab("Time(s)") + coord_cartesian(ylim = c(10,35))+theme_classic()
p1
ggsave(p1, width = 6, height = 4,filename=glue("../../Figures/Running_time//Setting1_zoom2_TM.pdf"))
```

# Plot setting2
Deep learning methods
```{r}
nn_methods = c("DeepLift", "GradientShap", "LRP" , "FeatureAblation", "Occlusion"  ,"Lime")
dl_cat <- c(rep("Deep learning - gradient based", 3), rep("Deep learning - perturbation", 3))
dl_cat_num =1
df <- data.frame()
for (method in nn_methods){
  time.res <- read.csv(glue("../../Result/Fs_marker/Nn/Setting2/{method}/Elapse_time_record.csv"))[,2:4]
  df <- rbind(df, cbind(time.res, method, dl_cat[dl_cat_num]))
  dl_cat_num = dl_cat_num +1
}
colnames(df) <- c("Time", "nGroups", "nCells","Method", "Category")
df.nn <- df
```

Traditional methods
```{r}
trad_methods = c( "runDESeq2", "runLimmavoom", "runScDD")
df <- data.frame()
for (method in trad_methods){
  n=1 # seed number 
  j=1
  while(j<=10){
    for(nGroups in c(10,20)){#seq(5,20,5)
      for (nCells in seq(50,250,50)){
        tmp_time = readRDS(glue("../../Result/Fs_marker/Traditional/Setting2//{method}/Res_{method}_Simulation_setting2_nGroups_{nGroups}_nCells_{nCells}_iteration{j}.rds"))$time
        df <- rbind(df,c(tmp_time, nGroups, nCells, method, "Traditional"))
        }
      }
    j=j+1
  }
  cat(glue("finished {method}"))
}
colnames(df) <- c("Time", "nGroups", "nCells","Method", "Category")
df.trad <- df
```


combine
```{r}
df.combine <- rbind(df.nn, df.trad)
df.combine$nGroups <- factor(df.combine$nGroups, levels = c(10,20))
df.combine$nCells <- factor(df.combine$nCells, levels = c(50,100,150,200,250))
df.combine$Method <- factor(df.combine$Method, levels = c(nn_methods, trad_methods))
df.combine$Time <- as.numeric(df.combine$Time)
```

```{r}
df.average <- aggregate(Time~Method+nGroups+nCells, data=df.combine, FUN=mean)
df.average
```

## 10 groups
Line plot, coloured by methods - 10 group
```{r,fig.height=3, fig.width=4}
p1 = ggplot(aes(x=nCells, y=Time, color=Method), data = df.average[df.average$nGroups == 10,]) + geom_line(aes(group=Method)) + geom_point(aes(color=Method)) +ylab("Time(s)") + coord_cartesian(ylim = c(0,5000))+theme_classic()
p1
ggsave(p1, width = 8, height = 5,filename=glue("../../Figures/Running_time//Setting2_TM_nGroups10.pdf"))
```


plot zoom - 10 group
```{r}
p1 = ggplot(aes(x=nCells, y=Time, color=Method), data = df.average[df.average$nGroups == 10, ]) + geom_line(aes(group=Method)) + geom_point(aes(color=Method)) +ylab("Time(s)") + coord_cartesian(ylim = c(0,650))+theme_classic()
p1
ggsave(p1, width = 8, height = 5,filename=glue("../../Figures/Running_time//Setting2_zoom_TM_nGroups10.pdf"))
```


plot zoom2 - 10 group
```{r}
p1 = ggplot(aes(x=nCells, y=Time, color=Method), data = df.average[df.average$nGroups == 10, ]) + geom_line(aes(group=Method)) + geom_point(aes(color=Method)) +ylab("Time(s)") + coord_cartesian(ylim = c(10,30))+theme_classic()
p1
ggsave(p1, width = 8, height = 5,filename=glue("../../Figures/Running_time//Setting2_zoom2_TM_nGroups10.pdf"))
```

## 20 groups
Line plot, coloured by methods - 20 group
```{r,fig.height=3, fig.width=4}
p1 = ggplot(aes(x=nCells, y=Time, color=Method), data = df.average[df.average$nGroups == 20,]) + geom_line(aes(group=Method)) + geom_point(aes(color=Method)) +ylab("Time(s)") + coord_cartesian(ylim = c(0,20000))+theme_classic()
p1
ggsave(p1, width = 8, height = 5,filename=glue("../../Figures/Running_time//Setting2_TM_nGroups20.pdf"))
```


plot zoom - 20 group
```{r}
p1 = ggplot(aes(x=nCells, y=Time, color=Method), data = df.average[df.average$nGroups == 20, ]) + geom_line(aes(group=Method)) + geom_point(aes(color=Method)) +ylab("Time(s)") + coord_cartesian(ylim = c(0,700))+theme_classic()
p1
ggsave(p1, width = 8, height = 5,filename=glue("../../Figures/Running_time//Setting2_zoom_TM_nGroups20.pdf"))
```


plot zoom2 - 20 group
```{r}
p1 = ggplot(aes(x=nCells, y=Time, color=Method), data = df.average[df.average$nGroups == 20, ]) + geom_line(aes(group=Method)) + geom_point(aes(color=Method)) +ylab("Time(s)") + coord_cartesian(ylim = c(15,40))+theme_classic()
p1
ggsave(p1, width = 8, height = 5,filename=glue("../../Figures/Running_time//Setting2_zoom2_TM_nGroups20.pdf"))
```